---
alway_keep_html: true
---

```{r message=FALSE, warning=FALSE,echo = FALSE, include=FALSE}
library(lubridate)
## load libraries
library(ggplot2)
library(shiny)
library(colourpicker)
library(readxl)
library(dplyr)
library(readr)
library(DT)
#library(extrafont)
#loadfonts()
library(knitr)
# glimpse(datBASE)
# dt <- data.frame(mon = c(10, 4), day = c(10, 4), year = c(2017, 2018))

# with(dt, ymd(paste(year, mon, day, sep = "-")))
#> [1] "2017-10-10" "2018-04-04"
#### these are now as csv files for each datasheet entry
#orginal excel in Raw_data file...
#no conversion to csv to aviod same data issues...

datPhD <- readr::read_csv(here::here("./data/PhDProjects.csv"))
datCouncil <- readr::read_csv(here::here("./data/CouncilProjects.csv"))
datInvert <- readr::read_csv(here::here("./data/InvertProjects.csv"))
## Full tasks database
datBASE <- bind_rows(datPhD, datCouncil, datInvert) %>%
  filter(project != "NA") %>%
    mutate(month = as.factor(month))

#17levels need sorting
# levels(datBASE$month) <- c("january","february", "march", "april", "may" ,"june", "july", "august","september", "october", "november", "december")

### to correct ggplot subset
datBASE1 <- datBASE  %>%
    dplyr::select(startDate,month, year, milestone, status, shortName, project) %>%
                 mutate(date = as.Date(startDate, "%d/%m/%y"))
# ,
#                        month = as.numeric(as.character(month)),
#                        year = as.numeric(year),
#                        milestone = as.factor(milestone),
#                        status = as.factor(status))
# glimpse(datBASE1)
# df$date <- with(df, ymd(sprintf('%04d%02d%02d', year, month, 1)))
df <- datBASE1

# library(lubridate)
# dt <- data.frame(mon = c(10, 4), day = c(10, 4), year = c(2017, 2018))
# with(dt, ymd(paste(year, mon, day, sep = "-")))
#> [1] "2017-10-10" "2018-04-04"

# datBASE1$date <- with(datBASE1, ymd(sprintf('%04d%02d%02d', year, month, 1)))
df <- df[with(df, order(date)), ]
# head(df)
text_offset <- 0.05


# Now let’s load in some data
#milestones is the demo data
#actions is my data

df <- readr::read_csv(here::here('./data/milestones.csv'))

# df$status
# names(datBASE)
### Subset dataframe


# > time.check= seq(as.Date('1985-01-01'),as.Date('2012-12-31'),by='day')
# > length(time.check)
# [1] 10227
# 
# DF <- data.frame(Year = rep(1985, 4), 
#                  Month = rep(1, 4), 
#                  Day = c(1,2,5,6), 
#                  Z = 7:10)
# DF
# #>   Year Month Day  Z
# #> 1 1985     1   1  7
# #> 2 1985     1   2  8
# #> 3 1985     1   5  9
# #> 4 1985     1   6 10
# colnames(DF)[4] <- "Data"
# DF
# #>   Year Month Day Data
# #> 1 1985     1   1    7
# #> 2 1985     1   2    8
# #> 3 1985     1   5    9
# #> 4 1985     1   6   10
# library(lubridate)
# #> 
# #> Attaching package: 'lubridate'
# #> The following object is masked from 'package:base':
# #> 
# #>     date
# DF$DATE <- make_date(year = DF$Year, month = DF$Month, day = DF$Day)
# DF
# #>   Year Month Day Data       DATE
# #> 1 1985     1   1    7 1985-01-01
# #> 2 1985     1   2    8 1985-01-02
# #> 3 1985     1   5    9 1985-01-05
# #> 4 1985     1   6   10 1985-01-06
# FullSeq <- seq.Date(from = min(DF$DATE), to = max(DF$DATE), by = 1)
# Missing <- FullSeq[!FullSeq %in% DF$DATE]
# Missing
# #> [1] "1985-01-03" "1985-01-04"

## First make up some mock data
# my_data <- data.frame(date = seq(as.Date("2010-01-01"), as.Date("2015-12-31"), 
#                                 by = "1 month"), 
#                      value = rnorm(72))
# 
# ## Remove some observations so we have an incomplete data set
# my_incomplete_data <- my_data[sort(sample(nrow(my_data), 60)), ]
# 
# ## Make a data frame with a full series of dates from the min date to the max date
# ## in the incomplete data frame
# full_dates <- seq(min(my_incomplete_data$date), max(my_incomplete_data$date), 
#                   by = "1 month")
# full_dates <- data.frame(date = full_dates)
# 
# ## Merge the complete data frame with the incomplete to fill in the dates and add 
# ## NAs for missing values
# my_complete_data <- merge(full_dates, my_incomplete_data, by = "date", 
#                           all.x = TRUE)

# NOT RUN {
## locale-specific version of the date
# format(Sys.Date(), "%a %b %d")
# }
# NOT RUN {
## read in date info in format 'ddmmmyyyy'
## This will give NA(s) in some locales; setting the C locale
## as in the commented lines will overcome this on most systems.
## lct <- Sys.getlocale("LC_TIME"); Sys.setlocale("LC_TIME", "C")
# x <- c("1jan1960", "2jan1960", "31mar1960", "30jul1960")
# z <- as.Date(x, "%d%b%Y")
## Sys.setlocale("LC_TIME", lct)
# z

## read in date/time info in format 'm/d/y'
# dates <- c("02/27/92", "02/27/92", "01/14/92", "02/28/92", "02/01/92")
# as.Date(dates, "%m/%d/%y")

## date given as number of days since 1900-01-01 (a date in 1989)
# as.Date(32768, origin = "1900-01-01")
## Excel is said to use 1900-01-01 as day 1 (Windows default) or
## 1904-01-01 as day 0 (Mac default), but this is complicated by Excel
## incorrectly treating 1900 as a leap year.
## So for dates (post-1901) from Windows Excel
# as.Date(35981, origin = "1899-12-30") # 1998-07-05
## and Mac Excel
# as.Date(34519, origin = "1904-01-01") # 1998-07-05
## (these values come from http://support.microsoft.com/kb/214330)

## Experiment shows that Matlab's origin is 719529 days before ours,
## (it takes the non-existent 0000-01-01 as day 1)
## so Matlab day 734373 can be imported as
# as.Date(734373, origin = "1970-01-01") - 719529 # 2010-08-23
## (value from
## http://www.mathworks.de/de/help/matlab/matlab_prog/represent-date-and-times-in-MATLAB.html)

## Time zone effect
# z <- ISOdate(2010, 04, 13, c(0,12)) # midnight and midday UTC
# as.Date(z) # in UTC
# }
# NOT RUN {
# ## these time zone names are common
# as.Date(z, tz = "NZ")
# as.Date(z, tz = "HST") # Hawaii
# }

# set Home directory > home = setwd(Sys.getenv("HOME")); >  > # make path to the csv file > fpath = file.path(home, "Desktop", "at0901.csv"); > # read the csv file > at0901 = read.csv(fpath, header=TRUE);
```


# Visualisation {.tabset}

Generally the concept is to create a baseline dataset of information and then extend this using `dataspice` to create a tidy format of data that can then be modelled and visualised using the `tidyverse` suite of tools.

[*Creating timeline charts in R (Generating Timeline charts: Blog online)*]()

### Action tasks

Table by the group of project month or something else???

#### Table 1

```{r}
table(datBASE1$month, datBASE1$project)
```
 
#### Table 2

```{r}
table(datBASE1$month, datBASE1$project, datBASE1$status)
```

To do this I have created a calendar for each key project/impact/aspect of short-term timeline, objectives, as well as, my career and life projection. To begin with I need to create timelines and other project goals under covid19. I have put this into a single dataset called `dat` here.

These figures can be generated using `ggplot` and other `tidyverse` approaches due to the implantation of the `dataspice` packages above. We will use *ggplot* function from *ggplot2* package to generate timeline charts. The following plots can be created using layers to detail charts.

## `ggplot2` {.tabset}

### Milestones timeline

"Coverting a dataframe into a timeline"

### Factoring

```{r}
#factoring
status_levels <- c("Complete", "On Target", "At Risk", "Critical")

status_colors <- c("#0070C0", "#00B050", "#FFC000", "#C00000")

df$status <- factor(df$status, levels=status_levels, ordered=TRUE)
```

### Direction

```{r}
library(lubridate)
df <- readr::read_csv(here::here('./data/milestones.csv'))
df$date <- with(df, ymd(sprintf('%04d%02d%02d', year, month, 1)))
#direction
positions <- c(0.5, -0.5, 1.0, -1.0, 1.5, -1.5)
directions <- c(1, -1)

line_pos <- data.frame(
    "date"=unique(df$date),
    "position"=rep(positions, length.out=length(unique(df$date))),
    "direction"=rep(directions, length.out=length(unique(df$date)))
)

df <- merge(x=df, y=line_pos, by="date", all = TRUE)
df <- df[with(df, order(date, status)), ]

df$month_count <- ave(df$date==df$date, df$date, FUN=cumsum)
text_offset <- 0.2

df$text_position <- (df$month_count * text_offset * df$direction) + df$position
head(df)
```


### Counts

```{r}
text_offset <- 0.2

df$month_count <- ave(df$date==df$date, df$date, FUN=cumsum)
df$text_position <- (df$month_count * text_offset * df$direction) + df$position
head(df)
```


### Buffering times


```{r eval = FALSE}
month_buffer <- 2

month_date_range <- seq(min(df$date) - months(month_buffer), max(df$date) + months(month_buffer), by='month')
month_format <- format(month_date_range, '%b')
month_df <- data.frame(month_date_range, month_format)
```


### December/January only

```{r eval = FALSE}
year_date_range <- seq(min(df$date) - months(month_buffer), max(df$date) + months(month_buffer), by='year')
year_date_range <- as.Date(
    intersect(
        ceiling_date(year_date_range, unit="year"),
        floor_date(year_date_range, unit="year")
    ),  origin = "1970-01-01"
)
year_format <- format(year_date_range, '%Y')
year_df <- data.frame(year_date_range, year_format)
```


### Interactivity

Shiny....

```{r include=FALSE}
library(shiny)
library(visNetwork)
# shiny::runApp(system.file("shiny", package = "visNetwork"))
```
